\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-05-05 static/tree.tex
going over appendix

\documentclass{article}
\usepackage{tikz}
\usetikzlibrary{trees}
\tikzstyle{densely dashdotted}=      [dash pattern=on 3pt off 1pt on \the\pgflinewidth off 1pt]
\tikzset{
  treenode/.style = {shape=circle, inner sep=1pt,
draw, align=center, fill, black
%top color=white, bottom color=blue!20
  },
  payoff/.style    = {align=center, inner sep=0.1em, text width=1.5em},
  left side node/.style={above left, inner sep=0.1em},
  right side node/.style={above right, inner sep=0.1em}
}

\begin{document}
\begin{tikzpicture}
  [
%grow                    = right,
sibling distance        = 25em,
level 2/.style          = {sibling distance=2cm},
level 3/.style          = {sibling distance=3.5cm},
level 4/.style          = {sibling distance=2cm},
level distance          = 6em,
every node/.style       = {font=\footnotesize},
%sloped
  ]
  \node [treenode] {} child{node[payoff] {$S_{L}, S_{T}$}
  child{node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=35] {$\frac{k-1}{N-2}\frac{k-2}{N-3}$}}
  child{node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=45] {$\frac{k-1}{N-2}\frac{N-k-1}{N-3}$}}
  child{ node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-45] {$\frac{N-k-1}{N-2}\frac{k-1}{N-3}$}}
  child{ node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-35, xshift=-.5cm] {$\frac{N-k-1}{N-2}\frac{N-k-2}{N-3}$}}
  edge from parent node[left side node] {$\frac{1}{1 - N}$}}
  child{node [treenode] {} 
  child{node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{M}$}
  child{node [payoff] {\\ $S_{L}, S_{T}$} edge from parent[densely dashdotted] node[left side node] {$\frac{1}{N-3}$}}
  child{node [treenode] {} 
  child{node [payoff] {\\ $S_{L}, S_{M} -  S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=35] {$\frac{k-2}{N-3}\frac{k-3}{N-4}$}}
  child{node [payoff] {\\ $S_{L}, S_{R} -  S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=45] {$\frac{N-k-1}{N-3}\frac{k-2}{N-4}$}}
  child{ node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-45] {$\frac{k-2}{N-3}\frac{N-k-1}{N-4}$}}
  child{ node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-35, xshift=-.5cm] {$\frac{N-k-1}{N-3}\frac{N-k-2}{N-4}$}}
  edge from parent node[right side node] {$1 - \frac{1}{N-3}$}}
  edge from parent node[left side node, rotate=35] {$\frac{k-1}{N-2}\frac{k-2}{N-3}$}}
  child{node [payoff] {\\ $S_{L}, S_{R} -  S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=45] {$\frac{k-1}{N-2}\frac{N-k-1}{N-3}$}}
  child{ node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-45] {$\frac{N-k-1}{N-2}\frac{k-1}{N-3}$}}
  child{ node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-35, xshift=-.5cm] {$\frac{N-k-1}{N-2}\frac{N-k-2}{N-3}$}
  edge from parent node[right side node, xshift=-3cm, yshift=2.1cm] {$1 - \frac{1}{1 - N}$}}};
\end{tikzpicture}
\end{document}

>>>>

\documentclass{standalone}
% \usetikzlibrary{trees}
% \tikzstyle{densely dashdotted}=      [dash pattern=on 3pt off 1pt on \the\pgflinewidth off 1pt]
% \tikzset{
%   treenode/.style = {shape=circle, inner sep=1pt,
% draw, align=center, fill, black
% %top color=white, bottom color=blue!20
%   },
%   payoff/.style    = {align=center, inner sep=0.1em, text width=1.5em},
%   left side node/.style={above left, inner sep=0.1em},
%   right side node/.style={above right, inner sep=0.1em}
% }

% \begin{document}
% \begin{tikzpicture}
%   [
% %grow                    = right,
% sibling distance        = 25em,
% level 2/.style          = {sibling distance=2cm},
% level 3/.style          = {sibling distance=3.5cm},
% level 4/.style          = {sibling distance=2cm},
% level distance          = 6em,
% every node/.style       = {font=\footnotesize},
% %sloped
%   ]
%   \node [treenode] {} child{node[payoff] {$S_{L}, S_{T}$}
%   child{node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=35] {$\frac{k-1}{N-2}\frac{k-2}{N-3}$}}
%   child{node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=45] {$\frac{k-1}{N-2}\frac{N-k-1}{N-3}$}}
%   child{ node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-45] {$\frac{N-k-1}{N-2}\frac{k-1}{N-3}$}}
%   child{ node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-35, xshift=-.5cm] {$\frac{N-k-1}{N-2}\frac{N-k-2}{N-3}$}}
%   edge from parent node[left side node] {$\frac{1}{1 - N}$}}
%   child{node [treenode] {} 
%   child{node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{M}$}
%   child{node [payoff] {\\ $S_{L}, S_{T}$} edge from parent[densely dashdotted] node[left side node] {$\frac{1}{N-3}$}}
%   child{node [treenode] {} 
%   child{node [payoff] {\\ $S_{L}, S_{M} -  S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=35] {$\frac{k-2}{N-3}\frac{k-3}{N-4}$}}
%   child{node [payoff] {\\ $S_{L}, S_{R} -  S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=45] {$\frac{N-k-1}{N-3}\frac{k-2}{N-4}$}}
%   child{ node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-45] {$\frac{k-2}{N-3}\frac{N-k-1}{N-4}$}}
%   child{ node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-35, xshift=-.5cm] {$\frac{N-k-1}{N-3}\frac{N-k-2}{N-4}$}}
%   edge from parent node[right side node] {$1 - \frac{1}{N-3}$}}
%   edge from parent node[left side node, rotate=35] {$\frac{k-1}{N-2}\frac{k-2}{N-3}$}}
%   child{node [payoff] {\\ $S_{L}, S_{R} -  S_{T}, S_{M}$} edge from parent[densely dashdotted] node[left side node, rotate=45] {$\frac{k-1}{N-2}\frac{N-k-1}{N-3}$}}
%   child{ node [payoff] {\\ $S_{L}, S_{M} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-45] {$\frac{N-k-1}{N-2}\frac{k-1}{N-3}$}}
%   child{ node [payoff] {\\ $S_{L}, S_{R} - S_{T}, S_{R}$} edge from parent[densely dashdotted] node[right side node, rotate=-35, xshift=-.5cm] {$\frac{N-k-1}{N-2}\frac{N-k-2}{N-3}$}
%   edge from parent node[right side node, xshift=-3cm, yshift=2.1cm] {$1 - \frac{1}{1 - N}$}}};
% \end{tikzpicture}
% \end{document}

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 7cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 1.9cm, level distance=2.8cm},
    level 3/.style = {sibling distance = 2cm, level distance=1.9cm},
    level 4/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm] $S_{R} - S_{R}$}] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
    edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm] $S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{R} - S_{R}$}] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
            child{ node [arn_n, rotate=-30] {} 
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
                    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent[densely dashdotted] node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
                    edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
            }
            edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}; 
\end{tikzpicture}
\end{document}
